---
title: "Lab 6"
author: "Nicholas Stout"
date: "November 8, 2018"
output: html_document
---
#Names
Nicholas Stout
#Summary
This is a data set of several years worth of Kickstarter data. Kickstarter is a website where people can post ideas they need money to find, and other people may donate to their cause. Summary of the variable,s from the Kaggle page:
ID - internal kickstarter id
name - name of project - A project is a finite work with a clear goal that you’d like to bring to life. Think albums, books, or films.
category - category
main_category - category of campaign
currency - currency used to support
deadline - deadline for crowdfunding
goal - fundraising goal - The funding goal is the amount of money that a creator needs to complete their project.
launched - date launched
pledged - amount pledged by "crowd"
state - Current condition the project is in
backers - number of backers
country - country pledged from
usd pledged - amount of money pledged
usd.pledged.real - (No description)
usd goal.real - Goal amount in USD 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
ks_data=read.csv("ks-projects-201801.csv")
```

```{r}
head(ks_data)
str(ks_data)
summary(ks_data)
ggplot(ks_data, aes(x=currency, y=goal))+geom_boxplot()
max = max(ks_data$goal)
filter(ks_data, goal == 100000000) %>% select(name)
```

We would like to explore this data to find what effects if a Kickstarter succeeds, looking at amount of time to pledge, the goal amount, and how it is effected by the category.

#cleaning
For cleaning, we would need to fix the date and time objects to the correct datatype. The notes on the last three variables (usd pledged, usd.pledged.real, usd goal.real) are ambiguous about what they are for exactly. Those may need to be converted by hand. ID should probably be converted to a factor as well. It appears there are around 36 with a goal of exactly 100,000,000. That may be the max on the site, however, because the ones I checked were legitimate.